Results

### 2023-09-06 03_analysis/02_results_summary.Rmd
updates

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, warning = F, message = F)
```

**Note**: Table 1 shows results with the imputed dataset. Table 2 shows results with the non-imputed dataset.

```{r, results='asis'}
load(
  paste0(getwd(), "/tab1.R")
)
reg.tab1 <- reg.tab
cat(reg.tab1)
```

```{r, results='asis'}
load(
  paste0(getwd(), "/tab2.R")
)
reg.tab2 <- reg.tab
cat(reg.tab2)
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, warning = F, message = F)
library(texreg)
library(estimatr)
```

**Note**: Table 1 shows full panel results with the imputed dataset. Table 2 shows full panel results with the non-imputed dataset. Tables 3-5 show OLS, IV, and Lewbel IV estimates by region, respectively, for the imputed dataset. Tables 6-8 show the same with the non-imputed dataset.

```{r, results='asis'}
load(
  paste0(getwd(), "/model_list1.R")
)
screenreg(model_list[7:10],
          include.ci = F,
          custom.coef.map = list(
            "aid" = "ODA",
            "debt" = "OOF",
            "lead_aid" = "ODA",
            "lead_debt" = "OOF"
          ))
```

```{r, results='asis'}
load(
  paste0(getwd(), "/tab2.R")
)
reg.tab2 <- reg.tab
reg.tab2
```
